---
title: "Final Project"
author: "Anamika and Robert"
date: '2022-09-12'
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
editor_options:
  markdown:
    wrap: 72
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.Import dataset diamonds from R

```{r}
library("ggplot2")
dm=diamonds;
```

2.  Summary Analysis. (Mean Median,Range,Quantile)

```{r}
head(dm)
names(dm)
dim(dm)
summary(dm)
```

a)  The dataset has 10 columns and 53940 rows.

b)  Categorical variables:- cut,, color, clarity

c)  Numeric Variables- carat, depth,table, price,x,y,z

Summary:

Carat: Min- 0.2, Maximum- 5.01 Mean- 0.7979, Median- 0.700 It is right
skewed because Mean\>Median.

depth: Min- 43.00, Maximum-79.00 Mean-61.75, Median-61.80

Price : Min-326, Maximum- 18823 Mean- 3933, Median-2401 It is right
skewed because Mean\>Median .

3.  Frequency Plot of categorical data

PLOT 1

```{r}
fig1_cut=ggplot(data=dm,aes(x=cut))+geom_bar(aes(x=cut, fill =cut))+
  ggtitle("FREQUENCY PLOT OF CUT PARAMETER")+
  xlab("CUT PARAMETER")+
  ylab("COUNT")
jpeg("fig1_cut.jpeg")
dev.off()
fig1_cut
```

Observations: The descending order on counts of diamonds according to
their cut parameter is as follows: Ideal\>Premium\>VeryGood\>Good\>Fair

PLOT 2

```{r}
fig2_color=ggplot(data=dm,aes(x=color))+geom_bar(aes(x=color, fill =color))+
  ggtitle("FREQUENCY PLOT OF COLOR PARAMETER")+
  xlab("COLOR PARAMETER")+
  ylab("COUNT")
jpeg("fig2_color.lpeg")
dev.off()
fig2_color
```

Observations: The descending order on counts of diamonds according to
their color parameter is as follows: G\>E\>F\>H\>D\>I\>J

PLOT 3

```{r}
fig3_clarity=ggplot(data=dm,aes(x=clarity))+geom_bar(aes(x=clarity,fill=clarity))+
  ggtitle("FREQUENCY PLOT OF CLARITY PARAMETER")+
  xlab("CLARITY PARAMETER")+
  ylab("COUNT")
jpeg("fig3_clarity")
dev.off()
fig3_clarity
```

Observations: The descending order on counts of diamonds according to
their clarity parameter is as follows:
SI1\>VS2\>SI2\>VS1\>VVS2\>VVS1\>IF\>I1 We see there are less numbers of
high clarity diamonds. It may be due to the difficulty in machining
diamonds to that extent.So, we see there are more number of SI1 and VS2
clarity diamonds as they are easy to produce.

4.Correlation and correlation graph

```{r}
names(dm)
```

Finding correlation between all numeric parameters i;e carat, depth,
table,x,y and z.

```{r}
cname=c("carat","depth","table","price","x","y","z")
dm_n=dm[cname]
cor(dm_n)
```

We will remove depth and table from our correlation analysis as their
correlation value is not significant with the other parameters that
means we cannot make out a linear relationships between them. Plotting
those with highest correlation vlaue's i;e carat,price,price,x,y,z

```{r}
c_f=dm_n[-c(2:3)]
cor(c_f)
```

We see that price has a highly positive linear relationship with carat
parameter. It also has a high positive linear relationship with X Y Z
parameters.

Correlation Plot showing scatter plot of each parameters with other
parameters.

PLOT 4

```{r}
fig4_cor=plot(c_f)
jpeg("fig4_cor.jpeg")
dev.off()
fig4_cor
```

4.  Do a Hypothesis testing on mean price. create a random sample of 30%
    data Take mean and make Hypothesis. Ho: mean =3000 H1:mean is not
    equal to 3000 and test it.

Creating a random sample 30% of the total population. Calculating the
mean of the sample and Hypothesis testing for H0: Sample mean is equal
to population mean ( Null Hypothesis) H1: Sample mean is not equal to
population mean.(Alternate Hypothesis)

```{r}
set.seed(1)
s1=sample(dm$price,size = 0.3*(length(dm$carat)),replace = FALSE)
ms1=mean(s1)
t.test(dm$price,mu=ms1)
```

Observation: P value = 0.1061 as p value \>alpha=0.05. we have no
sufficient evidence to reject H0 hypothesis.

Now taking Sample mean as 1000. sample mean = 1000 H0: population mean =
1000 (Null Hypothesis) H1: Population mean is not equal to 1000
(Alternate Hypothesis)

```{r}
ms2=1000;
t.test(dm$price,mu=ms2)
```

Here for sample mean 1000. pvalue \< 2.2e-16 \< alpha=0.05 We have
sufficient evidence to reject Null Hypothesis that is Population mean is
equal to 1000.
